Fig2

### 2020-02-21 analysis/figure-2.Rmd
better ylim

b11 <- makenewbargraph("hypothalamus", "female","eggs vs. chicks", 0, 800) +  labs(subtitle = "females", x = NULL, y = "Hyp. DEGS")
b21 <- makenewbargraph("pituitary", "female","eggs vs. chicks", 0, 800)  + labs(x = NULL, y = "Pit. DEGS")
b31 <- makenewbargraph("gonad", "female", "eggs vs. chicks", 0, 800) + labs(x = "eggs vs. chicks", y = "Gon. DEGS")   
b112131 <- plot_grid(b11,b21,b31, nrow = 3, rel_heights = c(1.1,1,1.1))

b12 <- makenewbargraph("hypothalamus", "male",  "eggs vs. chicks", 0, 800) + labs(subtitle = "males", x = NULL)+ 
  theme(axis.title.y = element_blank(), axis.text.y = element_blank())
b22 <- makenewbargraph("pituitary", "male", "eggs vs. chicks", 0, 800) + labs(x = NULL)+ 
  theme(axis.title.y = element_blank(), axis.text.y = element_blank())
b32 <- makenewbargraph("gonad", "male", "eggs vs. chicks", 0, 800) + labs(x = "eggs vs. chicks")   + 
  theme(axis.title.y = element_blank(), axis.text.y = element_blank())
b122232 <- plot_grid(b12, b22,b32, nrow = 3, rel_heights = c(1.1,1,1.1))

>>>>

b11 <- makenewbargraph("hypothalamus", "female","eggs vs. chicks", 0, 2500) +  labs(subtitle = "females", x = NULL, y = "Hyp. DEGS")
b21 <- makenewbargraph("pituitary", "female","eggs vs. chicks", 0, 2500)  + labs(x = NULL, y = "Pit. DEGS")
b31 <- makenewbargraph("gonad", "female", "eggs vs. chicks", 0, 2500) + labs(x = "eggs vs. chicks", y = "Gon. DEGS")   
b112131 <- plot_grid(b11,b21,b31, nrow = 3, rel_heights = c(1.1,1,1.1))

b12 <- makenewbargraph("hypothalamus", "male",  "eggs vs. chicks", 0, 2500) + labs(subtitle = "males", x = NULL)+ 
  theme(axis.title.y = element_blank(), axis.text.y = element_blank())
b22 <- makenewbargraph("pituitary", "male", "eggs vs. chicks", 0, 2500) + labs(x = NULL)+ 
  theme(axis.title.y = element_blank(), axis.text.y = element_blank())
b32 <- makenewbargraph("gonad", "male", "eggs vs. chicks", 0, 2500) + labs(x = "eggs vs. chicks")   + 
  theme(axis.title.y = element_blank(), axis.text.y = element_blank())
b122232 <- plot_grid(b12, b22,b32, nrow = 3, rel_heights = c(1.1,1,1.1))
